---
title: "Surprise/Amphitheater 1m Water Balance Model"
author: 
  - Stephen Huysman, shuysman@gmail.com
email: "shuysman@gmail.com"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    theme: cerulean
    number_sections: true
    toc: true
---


```{r setup, include=FALSE}
## Global options
## knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.height = 8, fig.width = 10)
```

All images can be clicked to view at full-size.

```{r}
library(terra)
library(tidyverse)
library(tidyterra)
library(ggspatial)
library(ggnewscale)
library(ggpubr)
library(gghighlight)
library(sf)

pal_greys <- hcl.colors(1000, "Grays")

grte_polys <- st_read("./data/StephenHuysman_GRTE_WBP_ModelingAreas/GRTE_WBP_ModelingAreas_merged.shp")

historical <- 1979:2022
load_historical <- function(filename) {
    r <- rast(filename)
    r <- r %>%
        clamp(lower = 0, values = FALSE) / 10 ## remove NAs and divide by ten (nps gridded wb is provided in units x 10)
    return(r)
}

end <- 2075:2099
load_gcm_mean <- function(filename) {
    r <- rast(filename)
    r <- r %>%
        subset(year(time(.)) %in% end) %>% ## Limit to end-century conditions
        mean() %>%
        clamp(lower = 0, values = FALSE) / 10 ## remove NAs and divide by ten (nps gridded wb is provided in units x 10)
    return(r)
}
```

# Core Areas

``` {r, core-areas, fig.cap = "YELL and GRTE Core Areas in WBP Climate Space.  This figure shows historical (2000-2019) AET/CWD average annual sums for known WBP occurences from the WPBR monitoring dataset.  Historical data for points within the GYE are highlighted in blue, the rest of the WBP range shown in grey.  Historical (green), RCP4.5 (darkviolet), and RCP8.5 (red) projections are also shown for the YELL and GRTE WBP core areas, as well as the Burroughs Creek planting site in the Shoshone NF.  RCP4.5 and RCP8.5 projections are ensemble averages provided by the 'summary layers' product from the NPS Gridded Water Balance dataset.  This figure visualizes the potential shifts in climate space that these sites could experience in the future, bracketed by the emission scenarios modeled under the RCP4.5 and RCP8.5 scenarios.  These data were generated from the 1km NPS gridded water balance model, and as such, absolute values of AET and CWD cannot be compared to the values generated from the 1m model presented here."}

### Coordinates for WBP "core areas".  These were basically randomly sampled w/in the
### polygons provided by YELL/GRTE
coords <- tribble(
    ~park, ~long, ~lat,
    "avalanche", -110.134243, 44.483019,
    "static_west", -110.807844, 43.675285,
    "static_east", -110.8015687, 43.6752922,
    "surprise", -110.7773406, 43.7295757,
    "burroughs", -109.6778113, 43.7061975
) %>% st_as_sf(coords = c("long", "lat"), crs = "EPSG:4326")

aet_summary_dir <- file.path("/media/smithers/shuysman/data/nps_gridded_wb/summary_layers/AET/")
cwd_summary_dir <- file.path("/media/smithers/shuysman/data/nps_gridded_wb/summary_layers/Deficit/")

aet_hist <- rast(file.path(aet_summary_dir, "historical/V_1_5_annual_gridmet_historical_AET_2000_2019_annual_means_cropped_units_mm.tif"))
names(aet_hist) <- "AET_hist"
cwd_hist <- rast(file.path(cwd_summary_dir, "historical/V_1_5_annual_gridmet_historical_Deficit_2000_2019_annual_means_cropped_units_mm.tif"))
names(cwd_hist) <- "CWD_hist"
aet_45 <- rast(file.path(aet_summary_dir, "rcp45/ensembles/ensemble_2070_2099_annual_rcp45_AET_units_mm.tif"))
names(aet_45) <- "AET_45"
cwd_45 <- rast(file.path(cwd_summary_dir, "rcp45/ensembles/ensemble_2070_2099_annual_rcp45_Deficit_units_mm.tif"))
names(cwd_45) <- "CWD_45"
aet_85 <- rast(file.path(aet_summary_dir, "rcp85/ensembles/ensemble_2070_2099_annual_rcp85_AET_units_mm.tif"))
names(aet_85) <- "AET_85"
cwd_85 <- rast(file.path(cwd_summary_dir, "rcp85/ensembles/ensemble_2070_2099_annual_rcp85_Deficit_units_mm.tif"))
names(cwd_85) <- "CWD_85"

wbp_points <- read_csv("/home/steve/OneDrive/whitebark/blister-rust/ej/SITE_LOCATIONS.csv") %>%
  drop_na(c("lat", "long")) %>%
  st_as_sf(coords = c("long", "lat"), crs = st_crs("EPSG:4326")) %>%
  bind_rows(coords) %>%
  st_transform(crs = st_crs(aet_hist))

wbp_points <- terra::extract(aet_hist, wbp_points, bind = TRUE)
wbp_points <- terra::extract(cwd_hist, wbp_points, bind = TRUE)
wbp_points <- terra::extract(aet_45, wbp_points, bind = TRUE)
wbp_points <- terra::extract(cwd_45, wbp_points, bind = TRUE)
wbp_points <- terra::extract(aet_85, wbp_points, bind = TRUE)
wbp_points <- terra::extract(cwd_85, wbp_points, bind = TRUE)

wbp_points %>%
    ggplot() +
    theme_bw() +
    geom_point(aes(x = CWD_hist, y = AET_hist), color = "azure4") +
    geom_point(data = filter(wbp_points, park == "GYE"), aes(x = CWD_hist, y = AET_hist), color = "deepskyblue3") +
    geom_point(data = filter(wbp_points, park %in% c("avalanche", "static_west", "surprise", "burroughs")), aes(x = CWD_hist, y = AET_hist, shape = park), size = 7, color = "green") +
    geom_point(data = filter(wbp_points, park %in% c("avalanche", "static_west", "surprise", "burroughs")), aes(x = CWD_45, y = AET_45, shape = park), size = 7, color = "darkviolet") +
    geom_point(data = filter(wbp_points, park %in% c("avalanche", "static_west", "surprise", "burroughs")), aes(x = CWD_85, y = AET_85, shape = park), size = 7, color = "red") +
    labs(title = "YELL and GRTE WBP Core Areas in WBP 'Climate Space'", x = "CWD", y = "AET")

```


# Surprise/Amphitheater


## Topographic & Soil Features
```{r surprise-poly, fig.cap = "Surprise/Amphitheater Direct Seeding Polygon with Hillshade from 1m LiDAR DEM"}
surprise_poly <- grte_polys[4,] %>% st_transform(crs = st_crs("EPSG:26912"))
surprise_elev <- rast("./data/input/surprise/dem/dem_nad83.tif")
surprise_slope <- rast("./data/input/surprise/dem/slope_nad83.tif")
surprise_aspect <- rast("./data/input/surprise/dem/aspect_nad83.tif")
surprise_hs <- rast("./data/input/surprise/dem/hillshade_nad83.tif")

slope_mask <- subst(surprise_slope > 60, FALSE, NA) ## HL Function can't take inputs >60 degrees for slope
soil_mask <- st_read("data/input/soil/grte_modelingareas_ssurgo.shp") %>% subset(fid %in% c(18, 20, 22)) ### soil type with NA soil depth, screws up WB calculations

ggplot() +
    geom_spatraster(data = surprise_hs, show.legend = FALSE) +
##    geom_spatraster(data = subset(tmmn$daily_minimum_temperature, 1)) +
    scale_fill_gradientn(colors = pal_greys, na.value = NA) +
    geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) +
    labs(title = "Surprise/Amphitheater with Hillshade") +
    annotation_north_arrow(aes(location = "tr")) +
    annotation_scale(aes(location = "br"))
```


``` {r surprise-statistics,  warning = FALSE, message = FALSE, echo = FALSE}
stats <- data.frame(elev_mean = zonal(surprise_elev, vect(surprise_poly), fun = "mean")[[1]],
                         elev_max = zonal(surprise_elev, vect(surprise_poly), fun = "max")[[1]],
                         elev_min = zonal(surprise_elev, vect(surprise_poly), fun = "min")[[1]],
                         slope_mean = zonal(surprise_slope, vect(surprise_poly), fun = "mean", na.rm = TRUE)[[1]],
                         slope_max = zonal(surprise_slope, vect(surprise_poly), fun = "max", na.rm = TRUE)[[1]],
                         slope_min = zonal(surprise_slope, vect(surprise_poly), fun = "min", na.rm = TRUE)[[1]],
                         aspect_mean = zonal(surprise_aspect, vect(surprise_poly), fun = "mean", na.rm = TRUE)[[1]]
                    )
knitr::kable(
    stats,
    digits = 2,
    caption = "Topographic Statistics of Surprise/Amphitheater Polygon")
```

This site contains areas with slope > 60°.  The heat-load function takes slopes from 0-60° as input, so slopes >60° will be masked in this analysis.

```{r surprise-soil, fig.cap = "Surprise/Amphitheater Soil Water Holding Capacity (WHC, mm) at 25 cm soil depth."}
surprise_soil <- rast("./data/input/surprise/soil/soil_whc_025.tif")

ggplot() +
    geom_spatraster(data = surprise_soil) +
    labs(title = "Surprise/Amphitheater Soil WHC (mm) to 25cm soil depth") +
    scale_fill_viridis_b() +
    geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) +
    annotation_north_arrow(aes(location = "tr")) +
    annotation_scale(aes(location = "br"))
```

## Historical Water Balance

``` {r, surprise-historical}
surprise_dir <- file.path("/media/smithers/shuysman/data/out/nps-wb/surprise/")
surprise_historical_dir <- file.path(surprise_dir, "historical/sums/")
surprise_projections_dir <- file.path(surprise_dir, "projections/sums/")

(crop_ext <- ext(surprise_elev) + c(-2, 1, -1, 1)) ## Get rid of weird, erroneous pixels on left edge inside NA border, only appeared on this site

surprise_historical_aet <- load_historical(list.files(surprise_historical_dir, pattern = ".*AET.*.nc", full.names = TRUE)) %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext)
surprise_historical_cwd <- load_historical(list.files(surprise_historical_dir, pattern = ".*Deficit.*.nc", full.names = TRUE)) %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext)

surprise_aet_1988 <- surprise_historical_aet %>% subset(year(time(.)) == 1988)
surprise_cwd_1988 <- surprise_historical_cwd %>% subset(year(time(.)) == 1988)

surprise_aet_2022 <- surprise_historical_aet %>% subset(year(time(.)) >= 2002 & year(time(.)) <= 2022) %>% mean()
surprise_cwd_2022 <- surprise_historical_cwd %>% subset(year(time(.)) >= 2002 & year(time(.)) <= 2022) %>% mean()
```

### Baseline

Historical climate data are average across the years 2002-2022.  This
represents historical "baseline" conditions against with other
climatic summaries can be compared.

```{r, surprise-baseline, fig.cap = "Surprise/Amphitheater Historical Water Balance (2002-2022)"}

ggplot() +
    geom_spatraster(data = surprise_aet_2022) +
    scale_fill_viridis_c(option = "D") +
    geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) +
    labs(title = "Surprise/Amphitheater 2002-2022 Average Annual AET", x = "", y = "") +
    annotation_north_arrow(aes(location = "tr")) +
    annotation_scale(aes(location = "br"))

ggplot() +
    geom_spatraster(data = surprise_cwd_2022) +
    scale_fill_viridis_c(option = "B") +
    geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) +
    labs(title = "Surprise/Amphitheater 2002-2022 Average Annual CWD", x = "", y = "") +
    annotation_north_arrow(aes(location = "tr")) +
    annotation_scale(aes(location = "br"))

```

### 1988 Drought Year

1988 is selected as an example of a drought year for the location.
This year was characterized by extreme drought levels leading to
widespread wildfires across the GYE.  This serves as an example of an
extreme year against which other climatic summaries can be compared.

``` {r, surprise-drought-year, fig.cap="Surprise/Amphitheater Drought Year (1988) annual AET and CWD"}

ggplot() +
    geom_spatraster(data = surprise_aet_1988) +
    scale_fill_viridis_c(option = "D") +
    geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) +
    labs(title = "Surprise/Amphitheater 1988 Annual AET (Drought Year)", x = "", y = "") +
    annotation_north_arrow(aes(location = "tr")) +
    annotation_scale(aes(location = "br"))

ggplot() +
    geom_spatraster(data = surprise_cwd_1988) +
    scale_fill_viridis_c(option = "B") +
    geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) +
    labs(title = "Surprise/Amphitheater 1988 Annual CWD (Drought Year)", x = "", y = "") +
    annotation_north_arrow(aes(location = "tr")) +
    annotation_scale(aes(location = "br"))
```


<!-- ## Projected Water Balance  -->


<!-- Four GCM/Emission Scenario combinations were selected to bracket the range of -->
<!-- plausible future climates based on 'Warm/Wet', 'Warm/Dry', 'Hot/Wet', -->
<!-- and 'Hot/Dry' scenarios determined by changes in annual Temperature -->
<!-- and Precipitation.  These show the most extreme projections of future -->
<!-- climate.  For visualizations of future AET and CWD, only the "best" -->
<!-- and "worst" case scenarios are showing for the sake of brevity. -->
<!-- Climate projections are summarized across the years 2075-2099 to -->
<!-- represent "end-of-century" conditions.  Given the long amounts of time -->
<!-- needed for WBP trees to reach reproductive maturity, this is -->
<!-- approximately the time period that trees planted today would be -->
<!-- producing cones. -->

<!-- | Future   | GCM           | Scenario | Note                                                                  | -->
<!-- |----------|---------------|----------|-----------------------------------------------------------------------| -->
<!-- | Warm Wet | MRI-CGCM3     | RCP8.5   |                                                                       | -->
<!-- | Hot Wet  | CanESM2       | RCP8.5   | 'Best-Case' AET Scenario (Highest)                                    | -->
<!-- | Warm Dry | MRI-CGCM3     | RCP4.5   | 'Worse-Case' AET Scenario (Lowest), 'Best-Case' CWD Scenario (Lowest) | -->
<!-- | Hot Dry  | HadGEM2-CC365 | RCP8.5   | 'Worse-Case' CWD Scenario (Highest)                                   | -->



<!-- ``` {r, surprise-projections, fig.height = 8, fig.width = 16, fig.cap = "Projected Water Balance"} -->
<!-- ## best_case_aet: hot_wet -->
<!-- ## worse_case_aet: warm_dry -->
<!-- ## best_case_cwd: warm_dry -->
<!-- ## worst_case_cwd: hot_dry -->

<!-- surprise_aet_warm_wet <- load_gcm_mean(file.path(surprise_projections_dir, "MRI-CGCM3_rcp85_AET_annual_sum.nc"))  %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext) -->
<!-- surprise_aet_hot_wet <- load_gcm_mean(file.path(surprise_projections_dir,"CanESM2_rcp85_AET_annual_sum.nc"))  %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext) -->
<!-- surprise_aet_warm_dry <- load_gcm_mean(file.path(surprise_projections_dir, "MRI-CGCM3_rcp45_AET_annual_sum.nc"))  %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext) -->
<!-- surprise_aet_hot_dry <- load_gcm_mean(file.path(surprise_projections_dir,"HadGEM2-CC365_rcp85_AET_annual_sum.nc"))  %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext) -->

<!-- surprise_aet_warm_wet_change <- (surprise_aet_warm_wet - surprise_aet_2022) / surprise_aet_2022 -->
<!-- surprise_aet_hot_wet_change <- (surprise_aet_hot_wet - surprise_aet_2022) / surprise_aet_2022 -->
<!-- surprise_aet_warm_dry_change <- (surprise_aet_warm_dry - surprise_aet_2022) / surprise_aet_2022 -->
<!-- surprise_aet_hot_dry_change <- (surprise_aet_hot_dry - surprise_aet_2022) / surprise_aet_2022 -->

<!-- surprise_cwd_warm_dry <- load_gcm_mean(file.path(surprise_projections_dir, "MRI-CGCM3_rcp45_Deficit_annual_sum.nc"))  %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext) -->
<!-- surprise_cwd_hot_dry <- load_gcm_mean(file.path(surprise_projections_dir,"HadGEM2-CC365_rcp85_Deficit_annual_sum.nc"))  %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext) -->
<!-- surprise_cwd_warm_wet <- load_gcm_mean(file.path(surprise_projections_dir, "MRI-CGCM3_rcp85_Deficit_annual_sum.nc"))  %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext) -->
<!-- surprise_cwd_hot_wet <- load_gcm_mean(file.path(surprise_projections_dir,"CanESM2_rcp85_Deficit_annual_sum.nc"))  %>% mask(soil_mask, inverse = TRUE) %>% mask(slope_mask, inverse = TRUE) %>% crop(crop_ext) -->

<!-- surprise_cwd_warm_dry_change <- (surprise_cwd_warm_dry - surprise_cwd_2022) / surprise_aet_2022 -->
<!-- surprise_cwd_hot_dry_change <- (surprise_cwd_hot_dry - surprise_cwd_2022) / surprise_aet_2022 -->
<!-- surprise_cwd_warm_wet_change <- (surprise_cwd_warm_wet - surprise_cwd_2022) / surprise_aet_2022 -->
<!-- surprise_cwd_hot_wet_change <- (surprise_cwd_hot_wet - surprise_cwd_2022) / surprise_aet_2022 -->

<!-- aet_hot_wet_plot <- ggplot() + -->
<!--     ggnewscale::new_scale_fill() + -->
<!--     geom_spatraster(data = surprise_aet_hot_wet) + -->
<!--     scale_fill_viridis_c(option = "D") + -->
<!--     geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) + -->
<!--     labs(title = "AET Hot-Wet ('Best-Case'/Highest)", x = "", y = "") + -->
<!--     annotation_north_arrow(aes(location = "tr")) + -->
<!--     annotation_scale(aes(location = "br")) -->

<!-- aet_warm_dry_plot <- ggplot() + -->
<!--     ggnewscale::new_scale_fill() + -->
<!--     geom_spatraster(data = surprise_aet_warm_dry) + -->
<!--     scale_fill_viridis_c(option = "D") + -->
<!--     geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) + -->
<!--     labs(title = "AET Warm-Dry ('Worst-Case'/Lowest)", x = "", y = "") + -->
<!--     annotation_north_arrow(aes(location = "tr")) + -->
<!--     annotation_scale(aes(location = "br")) -->

<!-- cwd_warm_dry_plot <- ggplot() + -->
<!--     ggnewscale::new_scale_fill() + -->
<!--     geom_spatraster(data = surprise_cwd_warm_dry) + -->
<!--     scale_fill_viridis_c(option = "B") + -->
<!--     geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) + -->
<!--     labs(title = "CWD Warm-Dry ('Best-Case'/Lowest)", x = "", y = "") + -->
<!--     annotation_north_arrow(aes(location = "tr")) + -->
<!--     annotation_scale(aes(location = "br")) -->

<!-- cwd_hot_dry_plot <- ggplot() + -->
<!--     ggnewscale::new_scale_fill() + -->
<!--     geom_spatraster(data = surprise_cwd_hot_dry) + -->
<!--     scale_fill_viridis_c(option = "B") + -->
<!--     geom_sf(data = surprise_poly, fill = NA, lwd = 1.5) + -->
<!--     labs(title = "CWD Hot-Dry ('Worst-Case'/Highest)", x = "", y = "") + -->
<!--     annotation_north_arrow(aes(location = "tr")) + -->
<!--     annotation_scale(aes(location = "br")) -->

<!-- ggarrange(aet_hot_wet_plot, aet_warm_dry_plot) -->
<!-- ggarrange(cwd_warm_dry_plot, cwd_hot_dry_plot) -->

<!-- ``` -->


<!-- ## Climate Summary -->

<!-- ```{r, surprise-climate-summary, fig.height = 6, fig.width = 8, fig.cap = "Surprise/Amphitheater Climate summaries.  AET and CWD distributions for all 1m pixels in the avalanche polygon are shown for 1988 (Drought Year), 2002-2022 (Historical Baseline), and 2075-2099 projections for 'Warm/Wet', 'Warm/Dry', 'Hot/Wet', 'Hot/Dry' scenarios"} -->
<!-- aet_df <- as.data.frame(surprise_aet_1988) -->
<!-- aet_df <- cbind(aet_df, as.data.frame(surprise_aet_2022)) -->
<!-- aet_df <- cbind(aet_df, as.data.frame(surprise_aet_warm_wet)) -->
<!-- aet_df <- cbind(aet_df, as.data.frame(surprise_aet_hot_wet)) -->
<!-- aet_df <- cbind(aet_df, as.data.frame(surprise_aet_warm_dry)) -->
<!-- aet_df <- cbind(aet_df, as.data.frame(surprise_aet_hot_dry)) -->
<!-- names(aet_df) = c("AET_1988", "AET_2022", "AET_warm_wet", "AET_hot_wet", "AET_warm_dry", "AET_hot_dry") -->
<!-- aet_df <- aet_df %>% -->
<!--     pivot_longer(cols = 1:6) -->

<!-- ggplot(aet_df) + -->
<!--     geom_boxplot(aes(name, value)) + -->
<!--     labs(title = "Surprise East AET", x = "Scenario", y = "Annual AET (mm)") -->

<!-- cwd_df <- as.data.frame(surprise_cwd_1988) -->
<!-- cwd_df <- cbind(cwd_df, as.data.frame(surprise_cwd_2022)) -->
<!-- cwd_df <- cbind(cwd_df, as.data.frame(surprise_cwd_warm_wet)) -->
<!-- cwd_df <- cbind(cwd_df, as.data.frame(surprise_cwd_hot_wet)) -->
<!-- cwd_df <- cbind(cwd_df, as.data.frame(surprise_cwd_warm_dry)) -->
<!-- cwd_df <- cbind(cwd_df, as.data.frame(surprise_cwd_hot_dry)) -->
<!-- names(cwd_df) = c("CWD_1988", "CWD_2022", "CWD_warm_wet", "CWD_hot_wet", "CWD_warm_dry", "CWD_hot_dry") -->
<!-- cwd_df <- cwd_df %>% -->
<!--     pivot_longer(cols = 1:6) -->

<!-- ggplot(cwd_df) + -->
<!--     geom_boxplot(aes(name, value)) + -->
<!--     labs(title = "Surprise East CWD", x = "Scenario", y = "Annual CWD (mm)") -->

<!-- ``` -->

<!-- # Export Files -->
```{r, export, eval = F, include = F}
# Save files for Libby

writeRaster(surprise_aet_2022, "for_libby/surprise/surprise_aet_2002-2022.tif", overwrite = TRUE)
writeRaster(surprise_cwd_2022, "for_libby/surprise/surprise_cwd_2002-2022.tif", overwrite = TRUE)
## writeRaster(surprise_aet_hot_wet_change, "for_libby/surprise/surprise_aet_hot_wet_change.tif", overwrite = TRUE)
## writeRaster(surprise_cwd_hot_dry_change, "for_libby/surprise/surprise_cwd_hot_dry_change.tif", overwrite = TRUE)
## writeRaster(surprise_aet_hot_wet, "for_libby/surprise/surprise_aet_hot_wet.tif", overwrite = TRUE)
## writeRaster(surprise_cwd_hot_dry, "for_libby/surprise/surprise_cwd_hot_dry.tif", overwrite = TRUE)

```

```{js, echo=FALSE}
var elements = document.getElementsByTagName('img');
for(var i = 0, len = elements.length; i < len; i++) {
    elements[i].onclick = function () {
        window.open(this.src, '_blank');
    }
}
```
