---
title: "NPS Gridded Water Balance Analysis"
subtitle: "Example Report - Washburn Test Site"
author: "Stephen Huysman"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    includes:
      in_header: null
  pdf_document:
    toc: true
    latex_engine: xelatex
---

```{css lightbox-css, echo=FALSE}
/* Lightbox overlay */
.lightbox-overlay {
  display: none;
  position: fixed;
  top: 0; left: 0;
  width: 100%; height: 100%;
  background: rgba(0,0,0,0.85);
  z-index: 9999;
  cursor: zoom-out;
  justify-content: center;
  align-items: center;
}
.lightbox-overlay.active { display: flex; }
.lightbox-overlay img {
  max-width: 95%;
  max-height: 95%;
  box-shadow: 0 0 30px rgba(0,0,0,0.5);
}
/* Make chunk images look clickable */
.main-container img { cursor: zoom-in; }
```

```{js lightbox-js, echo=FALSE}
document.addEventListener("DOMContentLoaded", function() {
  // Create overlay
  var overlay = document.createElement("div");
  overlay.className = "lightbox-overlay";
  var fullImg = document.createElement("img");
  overlay.appendChild(fullImg);
  document.body.appendChild(overlay);

  overlay.addEventListener("click", function() {
    overlay.classList.remove("active");
  });

  // Attach click handlers to all images inside the main content
  document.querySelectorAll(".main-container img").forEach(function(img) {
    img.addEventListener("click", function() {
      fullImg.src = img.src;
      overlay.classList.add("active");
    });
  });
});
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8,
  dpi = 150
)
```

This is an example notebook that demonstrates how to visualize and analyze
output from the NPS Gridded Water Balance Model using the included Mt. Washburn
test site. It can be adapted for reporting on additional sites of interest by
changing the site name, paths, and analysis parameters in the Configuration
section below.

> **Important:** Model output values are stored as **mm x 10** (16-bit integer
> compression). All values must be **divided by 10** to obtain results in mm.
> The data loading functions in this notebook handle this conversion
> automatically.

# Prerequisites

This notebook requires three data sources. The macroclimate figure will be
skipped if sources 2 or 3 are not available; all other sections require only
source 1.

## 1. Model inputs and output (required)

Model input data (1 m DEM, shapefile, soil data) are stored in the project
repository using Git LFS.

```bash
# Clone the repository and check out the ubuntu-vm branch
git clone -b ubuntu-vm https://github.com/shuysman/nps-microclimate-water-balance.git
cd nps-microclimate-water-balance

# Pull large files tracked by Git LFS (DEM, shapefiles, soil, etc.)
git lfs pull
```

After cloning, the input data will be in `data/input/test/`. You must run
`git lfs pull` to retrieve the actual file contents -- without it, LFS-tracked
files will only contain pointer stubs.

**Model output** (annual sum NetCDF files in `output/test/sums/`) is not stored
in the repository and must be generated by running the model. See
`water_balance_readme.txt` in the project root for the full workflow. If running
the model on a remote virtual machine, retrieve the output files via SFTP (or
similar) and place them in `output/test/sums/` before running this notebook.

## 2. NPS 1 km summary layers (optional, for macroclimate figure)

The macroclimate figure requires NPS 1 km Gridded Water Balance summary layers.
Download the files listed below from the public S3 bucket, preserving the
subdirectory structure, and place them in `reports/summary_layers/` (or symlink
that path to an existing local copy). Alternatively, update `summary_layers_dir`
in the Configuration section to point elsewhere.

<http://screenedcleanedsummaries.s3-website-us-west-2.amazonaws.com/>

```
summary_layers/
├── AET/
│   ├── historical/
│   │   └── V_1_5_annual_gridmet_historical_AET_2000_2019_annual_means_cropped_units_mm.tif
│   ├── rcp45/
│   │   └── ensembles/
│   │       └── ensemble_2070_2099_annual_rcp45_AET_units_mm.tif
│   └── rcp85/
│       └── ensembles/
│           └── ensemble_2070_2099_annual_rcp85_AET_units_mm.tif
└── Deficit/
    ├── historical/
    │   └── V_1_5_annual_gridmet_historical_Deficit_2000_2019_annual_means_cropped_units_mm.tif
    ├── rcp45/
    │   └── ensembles/
    │       └── ensemble_2070_2099_annual_rcp45_Deficit_units_mm.tif
    └── rcp85/
        └── ensembles/
            └── ensemble_2070_2099_annual_rcp85_Deficit_units_mm.tif
```

Set `eval=TRUE` in the chunk below to download via `wget`, or copy the commands
into a terminal:

```{bash download-summary-layers, eval=FALSE}
mkdir -p summary_layers/AET/historical
mkdir -p summary_layers/AET/rcp45/ensembles
mkdir -p summary_layers/AET/rcp85/ensembles
mkdir -p summary_layers/Deficit/historical
mkdir -p summary_layers/Deficit/rcp45/ensembles
mkdir -p summary_layers/Deficit/rcp85/ensembles

BASE_URL="http://screenedcleanedsummaries.s3-website-us-west-2.amazonaws.com"

wget "${BASE_URL}/AET/historical/V_1_5_annual_gridmet_historical_AET_2000_2019_annual_means_cropped_units_mm.tif" \
  -O summary_layers/AET/historical/V_1_5_annual_gridmet_historical_AET_2000_2019_annual_means_cropped_units_mm.tif

wget "${BASE_URL}/Deficit/historical/V_1_5_annual_gridmet_historical_Deficit_2000_2019_annual_means_cropped_units_mm.tif" \
  -O summary_layers/Deficit/historical/V_1_5_annual_gridmet_historical_Deficit_2000_2019_annual_means_cropped_units_mm.tif

wget "${BASE_URL}/AET/rcp45/ensembles/ensemble_2070_2099_annual_rcp45_AET_units_mm.tif" \
  -O summary_layers/AET/rcp45/ensembles/ensemble_2070_2099_annual_rcp45_AET_units_mm.tif

wget "${BASE_URL}/Deficit/rcp45/ensembles/ensemble_2070_2099_annual_rcp45_Deficit_units_mm.tif" \
  -O summary_layers/Deficit/rcp45/ensembles/ensemble_2070_2099_annual_rcp45_Deficit_units_mm.tif

wget "${BASE_URL}/AET/rcp85/ensembles/ensemble_2070_2099_annual_rcp85_AET_units_mm.tif" \
  -O summary_layers/AET/rcp85/ensembles/ensemble_2070_2099_annual_rcp85_AET_units_mm.tif

wget "${BASE_URL}/Deficit/rcp85/ensembles/ensemble_2070_2099_annual_rcp85_Deficit_units_mm.tif" \
  -O summary_layers/Deficit/rcp85/ensembles/ensemble_2070_2099_annual_rcp85_Deficit_units_mm.tif
```

## 3. WBP monitoring locations (optional, for macroclimate figure)

The macroclimate figure uses whitebark pine monitoring locations
(`SITE_LOCATIONS.csv`) from the white pine blister rust monitoring dataset
(Huysman *et al.*, in prep) to plot the species' bioclimatic niche. **This
dataset is not publicly available.** Contact Erin Shanahan for permission before
sharing or redistributing. Place the file at `reports/SITE_LOCATIONS.csv` (or
symlink it), or update `wbp_points_file` in the Configuration section to point
elsewhere.

# Configuration

```{r config}
library(here)

## ------------------------------------------------------------------
## USER-CONFIGURABLE PATHS
## ------------------------------------------------------------------

## 1 m site-level model output (from output/{site}/sums/)
site_output_dir <- here("output", "test", "sums")

## NPS 1 km summary layers for the macroclimate figure (see Prerequisites)
summary_layers_dir <- here("reports", "summary_layers")

## Whitebark pine monitoring locations (see Prerequisites)
wbp_points_file <- here("reports", "SITE_LOCATIONS.csv")

## ------------------------------------------------------------------
## SITE
## ------------------------------------------------------------------
site_name    <- "test"          # directory name in data/input/ and output/
display_name <- "Mt. Washburn"  # display name used in figure titles
sites        <- read.csv(here("src", "sites.csv"))
site_shapefile <- here("data", "input", site_name, "shapefile", "sample.shp")

## ------------------------------------------------------------------
## ANALYSIS PARAMETERS
## ------------------------------------------------------------------

## Time periods
drought_year <- 1988
hist_years   <- 2004:2024
end_years    <- 2075:2099

## Planting site selection: number of cells to select for highest
## AET / lowest CWD. The algorithm independently selects the
## n_cells with highest AET and the n_cells with lowest CWD, then
## takes their intersection. Choosing n_cells is trial and error:
## too low and the two sets won't overlap (no pixels selected);
## too high and it includes locations with unsuitable AET or CWD.
n_cells <- 100000
```

# Libraries and Setup

```{r libraries}
library(terra)
library(tidyverse)
library(tidyterra)
library(lubridate)
library(glue)
library(sf)
library(ggpubr)
library(maptiles)

terraOptions(progress = 0)
```

*Note: all figures in this report can be clicked to enlarge.*

# Introduction

The suitability of a planting site is assessed using a water balance model. The
biophysical environment of plants is characterized by Actual Evapotranspiration
(AET)---a measure of plant water use and favorable growing conditions---and
Climatic Water Deficit (CWD)---a measure of drought stress. As indicators of
plant water use (AET) and plant water need (CWD), these two variables are more
robust predictors of vegetation distributions than other climate variables such
as temperature or precipitation and are well correlated with vegetation
distributions across local to continental spatial scales (Stephenson 1998).

First, the broad-scale macroclimatic suitability of the site is assessed using
the 1 km NPS Gridded Water Balance summary layers by comparing historical and
projected water balance. Then, the high-resolution 1 m water balance model
output is used to assess microclimatic variability within the study area.

# Model Inputs

The water balance model requires a 1 m DEM (reprocessed into slope and aspect),
soil water holding capacity, and Jennings snow coefficients. These are the
preprocessed inputs for the study area produced by `00_prep_data.R`.

```{r input-dem, fig.width=12, fig.height=4}
dem <- rast(here("data", "input", site_name, "dem", "dem_nad83.tif"))
slope <- rast(here("data", "input", site_name, "dem", "slope_nad83.tif"))
aspect <- rast(here("data", "input", site_name, "dem", "aspect_nad83.tif"))
hillshade <- rast(here("data", "input", site_name, "dem", "hillshade_nad83.tif"))

p_dem <- ggplot() +
  geom_spatraster(data = dem) +
  scale_fill_viridis_c(option = "D") +
  labs(title = "Elevation", fill = "m") +
  theme_minimal()

p_slope <- ggplot() +
  geom_spatraster(data = slope) +
  scale_fill_viridis_c(option = "E") +
  labs(title = "Slope", fill = "radians") +
  theme_minimal()

p_aspect <- ggplot() +
  geom_spatraster(data = aspect) +
  scale_fill_gradientn(colours = c("blue", "green", "red", "yellow", "blue"),
                       limits = c(0, 360)) +
  labs(title = "Aspect", fill = "degrees") +
  theme_minimal()

ggarrange(p_dem, p_slope, p_aspect, ncol = 3)
```

```{r input-soil-jennings, fig.width=10, fig.height=4}
soil_whc <- rast(here("data", "input", site_name, "soil", "soil_whc_025.tif"))
jennings <- rast(here("data", "input", site_name, "jennings_t50_coefficients.tif"))

p_soil <- ggplot() +
  geom_spatraster(data = soil_whc) +
  scale_fill_viridis_c(option = "C") +
  labs(title = "Soil water holding capacity", fill = "mm") +
  theme_minimal()

p_jennings <- ggplot() +
  geom_spatraster(data = jennings) +
  scale_fill_viridis_c(option = "A") +
  labs(title = "Jennings T50 snow coefficients", fill = "T50") +
  theme_minimal()

ggarrange(p_soil, p_jennings, ncol = 2)
```

```{r input-hillshade, fig.width=6, fig.height=6}
ggplot() +
  geom_spatraster(data = hillshade) +
  scale_fill_gradient(low = "black", high = "white", guide = "none") +
  geom_sf(data = terra::vect(site_shapefile), fill = NA, lwd = 1, color = "red") +
  labs(title = "Hillshade with study area boundary") +
  theme_minimal()
```

# Load 1 m Model Output

```{r load-data}
scenarios <- tribble(
  ~gcm,              ~scenario,     ~label,
  "gridmet",         "historical",  "historical",
  "gridmet",         "historical",  "drought-year",
  "MRI-CGCM3",       "rcp85",       "warm-wet",
  "MRI-CGCM3",       "rcp45",       "warm-dry",
  "HadGEM2-CC365",   "rcp85",       "hot-dry",
  "CanESM2",         "rcp85",       "hot-wet"
)

load_historical_mean <- function(filename) {
  r <- rast(filename)
  r <- r %>%
    subset(year(time(.)) %in% hist_years) %>%
    mean() %>%
    clamp(lower = 0, values = FALSE) / 10
  return(r)
}

load_gcm_mean <- function(filename) {
  r <- rast(filename)
  time(r) <- seq(ymd("2006-07-02"), ymd("2099-07-02"), by = "1 year")
  r <- r %>%
    subset(year(time(.)) %in% end_years) %>%
    mean() %>%
    clamp(lower = 0, values = FALSE) / 10
  return(r)
}

site_poly <- terra::vect(site_shapefile)

aet_data <- rast()
cwd_data <- rast()

for (i in seq_len(nrow(scenarios))) {
  scenario <- scenarios$scenario[i]
  gcm      <- scenarios$gcm[i]
  label    <- scenarios$label[i]

  if (scenario == "historical") {
    aet_file <- file.path(site_output_dir, "historical_gridmet_AET_annual_sum.nc")
    cwd_file <- file.path(site_output_dir, "historical_gridmet_Deficit_annual_sum.nc")

    if (label == "historical") {
      r_aet <- load_historical_mean(aet_file)
      r_cwd <- load_historical_mean(cwd_file)
    } else if (label == "drought-year") {
      r_aet <- rast(aet_file)
      r_cwd <- rast(cwd_file)
      r_aet <- subset(r_aet, year(time(r_aet)) == drought_year) / 10
      r_cwd <- subset(r_cwd, year(time(r_cwd)) == drought_year) / 10
    }
  } else {
    aet_file <- file.path(site_output_dir, glue("{gcm}_{scenario}_AET_annual_sum.nc"))
    cwd_file <- file.path(site_output_dir, glue("{gcm}_{scenario}_Deficit_annual_sum.nc"))
    r_aet <- load_gcm_mean(aet_file)
    r_cwd <- load_gcm_mean(cwd_file)
  }

  names(r_aet) <- label
  names(r_cwd) <- label

  add(aet_data) <- r_aet
  add(cwd_data) <- r_cwd
}

site_poly <- project(site_poly, crs(aet_data))
```

# Planting Site Macroclimate

Planting suitability is evaluated at a macroclimate (1 km) scale to compare the
study site to the broader landscape. Historical (2000--2019) and ensemble
end-of-century (2070--2099) RCP 4.5 and RCP 8.5 averages of annual AET and CWD
are retrieved from the NPS 1 km Gridded Water Balance summary layers.

```{r macroclimate, fig.width=10, fig.height=8, eval=dir.exists(summary_layers_dir) && file.exists(wbp_points_file)}
aet_summary_dir <- file.path(summary_layers_dir, "AET")
cwd_summary_dir <- file.path(summary_layers_dir, "Deficit")

aet <- rast(file.path(aet_summary_dir, "historical/V_1_5_annual_gridmet_historical_AET_2000_2019_annual_means_cropped_units_mm.tif"))
names(aet) <- "AET"
cwd <- rast(file.path(cwd_summary_dir, "historical/V_1_5_annual_gridmet_historical_Deficit_2000_2019_annual_means_cropped_units_mm.tif"))
names(cwd) <- "CWD"
aet_45 <- rast(file.path(aet_summary_dir, "rcp45/ensembles/ensemble_2070_2099_annual_rcp45_AET_units_mm.tif"))
names(aet_45) <- "AET_45"
cwd_45 <- rast(file.path(cwd_summary_dir, "rcp45/ensembles/ensemble_2070_2099_annual_rcp45_Deficit_units_mm.tif"))
names(cwd_45) <- "CWD_45"
aet_85 <- rast(file.path(aet_summary_dir, "rcp85/ensembles/ensemble_2070_2099_annual_rcp85_AET_units_mm.tif"))
names(aet_85) <- "AET_85"
cwd_85 <- rast(file.path(cwd_summary_dir, "rcp85/ensembles/ensemble_2070_2099_annual_rcp85_Deficit_units_mm.tif"))
names(cwd_85) <- "CWD_85"

wbp_points <- read_csv(wbp_points_file) %>%
  bind_rows(tibble(network = "YELL", park = "YELL", long = sites$lon, lat = sites$lat, site = sites$site)) %>%
  drop_na(c("lat", "long")) %>%
  st_as_sf(coords = c("long", "lat"), crs = st_crs("EPSG:4326")) %>%
  st_transform(crs = st_crs(aet))

wbp_points <- terra::extract(aet, wbp_points, bind = TRUE)
wbp_points <- terra::extract(cwd, wbp_points, bind = TRUE)
wbp_points <- terra::extract(aet_45, wbp_points, bind = TRUE)
wbp_points <- terra::extract(cwd_45, wbp_points, bind = TRUE)
wbp_points <- terra::extract(aet_85, wbp_points, bind = TRUE)
wbp_points <- terra::extract(cwd_85, wbp_points, bind = TRUE)

ggplot(wbp_points) +
  geom_point(aes(x = CWD, y = AET), color = "darkgrey") +
  geom_point(data = filter(wbp_points, park == "GYE"), aes(x = CWD, y = AET), color = "royalblue1") +
  geom_point(size = 6, data = filter(wbp_points, park == "YELL"), aes(x = CWD, y = AET, shape = site, color = "black")) +
  geom_point(size = 6, data = filter(wbp_points, park == "YELL"), aes(x = CWD_45, y = AET_45, shape = site, color = "orange")) +
  geom_point(size = 6, data = filter(wbp_points, park == "YELL"), aes(x = CWD_85, y = AET_85, shape = site, color = "red")) +
  scale_color_manual(name = "Scenario (color)",
                    values = c("black"="black",
                               "orange"="orange",
                               "red"="red"),
                    labels=c("Historical 2000\u20132019","RCP45 2070\u20132099","RCP85 2070\u20132099")) +
  labs(x = "Annual CWD (mm)", y = "Annual AET (mm)", shape = "Site (shape)")
```

```{r macroclimate-skip-msg, eval=!dir.exists(summary_layers_dir) || !file.exists(wbp_points_file), results='asis'}
msg <- "**Macroclimate figure skipped.** Missing data:\n\n"
if (!dir.exists(summary_layers_dir))
  msg <- paste0(msg, "- `summary_layers_dir` not found at `", summary_layers_dir, "`\n")
if (!file.exists(wbp_points_file))
  msg <- paste0(msg, "- `wbp_points_file` not found at `", wbp_points_file, "`\n")
cat(msg)
```

# Planting Site Microclimate

The following figures show the microclimatic variability in average annual AET
and CWD for historical and projected climate scenarios. The 1988 drought year,
where record low precipitation resulted in widespread drought and wildfire across
the Greater Yellowstone Ecosystem, shows much lower annual AET and much higher
CWD compared to the 2004--2024 historical baseline.

Four projected climate scenarios bracket extremes of changes in annual
temperature and precipitation: *warm-wet* (MRI-CGCM3/RCP8.5), *warm-dry*
(MRI-CGCM3/RCP4.5), *hot-dry* (HadGEM2-CC365/RCP8.5), and *hot-wet*
(CanESM2/RCP8.5).

## Microclimate AET

```{r microclimate-aet, fig.width=10, fig.height=6}
aet_df <- aet_data %>%
  mask(site_poly) %>%
  as.data.frame(wide = FALSE)
aet_df$site <- display_name

aet_df <- aet_df %>%
  mutate(
    layer = factor(layer, levels = c(
      "historical", "drought-year", "warm-wet", "warm-dry", "hot-dry", "hot-wet"
    )),
    time = if_else(
      layer %in% c("historical", "drought-year"),
      "historical", "projection"
    )
  )

ggplot(aet_df) +
  geom_boxplot(aes(x = layer, y = values, color = site)) +
  labs(color = "Site", x = "Scenario", y = "Average annual AET (mm)") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  facet_wrap(~time, scales = "free_x")
```

## Microclimate CWD

```{r microclimate-cwd, fig.width=10, fig.height=6}
cwd_df <- cwd_data %>%
  mask(site_poly) %>%
  as.data.frame(wide = FALSE)
cwd_df$site <- display_name

cwd_df <- cwd_df %>%
  mutate(
    layer = factor(layer, levels = c(
      "historical", "drought-year", "warm-wet", "warm-dry", "hot-dry", "hot-wet"
    )),
    time = if_else(
      layer %in% c("historical", "drought-year"),
      "historical", "projection"
    )
  )

ggplot(cwd_df) +
  geom_boxplot(aes(x = layer, y = values, color = site)) +
  labs(color = "Site", x = "Scenario", y = "Average annual CWD (mm)") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  facet_wrap(~time, scales = "free_x")
```

# Modeled 1 m Water Balance

Modeled 1 m water balance shows significant variability in microclimates created
by local terrain features. Spatial patterns of AET and CWD are consistent across
time periods: more northern exposures and higher soil water holding capacities
maximize AET and minimize CWD, while more southern exposures and lower soil
water holding capacities minimize AET and maximize CWD.

```{r wb-color-scales}
max_aet <- max(minmax(mask(aet_data, site_poly)))
max_cwd <- max(minmax(mask(cwd_data, site_poly)))

aet_scale <- scale_fill_viridis_c(option = "D", limits = c(0, max_aet))
cwd_scale <- scale_fill_viridis_c(option = "B", limits = c(0, max_cwd))
```

## AET Maps

```{r wb-aet-maps, fig.width=8, fig.height=12}
aet_masked <- mask(aet_data, site_poly)

ggplot() +
  geom_spatraster(data = aet_masked) +
  aet_scale +
  facet_wrap(~lyr, ncol = 2) +
  labs(
    title = glue("{display_name} average annual AET"),
    fill = "Annual AET (mm)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)
  )
```

## CWD Maps

```{r wb-cwd-maps, fig.width=8, fig.height=12}
cwd_masked <- mask(cwd_data, site_poly)

ggplot() +
  geom_spatraster(data = cwd_masked) +
  cwd_scale +
  facet_wrap(~lyr, ncol = 2) +
  labs(
    title = glue("{display_name} average annual CWD"),
    fill = "Annual CWD (mm)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)
  )
```

# Planting Site Selection

Algorithmically selected planting locations maximize AET and minimize CWD under
end-of-century (2075--2099) projections. The algorithm selects cells with the
highest AET and lowest CWD and takes their intersection to identify locations
that optimize both conditions simultaneously. The number of cells to select
(`n_cells`) can be adjusted based on planting objectives and risk tolerance.

```{r planting-selection}
## --- Worst-case (hot-dry) scenario ---
hot_dry_aet <- aet_data %>% subset("hot-dry") %>% mask(site_poly)
hot_dry_cwd <- cwd_data %>% subset("hot-dry") %>% mask(site_poly)

n_valid <- sum(!is.na(values(hot_dry_aet)))
n_select <- min(n_cells, n_valid)

highest_aet_worst <- selectHighest(hot_dry_aet, n = n_select, low = FALSE)
lowest_cwd_worst  <- selectHighest(hot_dry_cwd, n = n_select, low = TRUE)
union_worst       <- lowest_cwd_worst & highest_aet_worst

## --- Best-case (warm-dry) scenario ---
warm_dry_aet <- aet_data %>% subset("warm-dry") %>% mask(site_poly)
warm_dry_cwd <- cwd_data %>% subset("warm-dry") %>% mask(site_poly)

n_valid_best <- sum(!is.na(values(warm_dry_aet)))
n_select_best <- min(n_cells, n_valid_best)

highest_aet_best <- selectHighest(warm_dry_aet, n = n_select_best, low = FALSE)
lowest_cwd_best  <- selectHighest(warm_dry_cwd, n = n_select_best, low = TRUE)
union_best       <- lowest_cwd_best & highest_aet_best
```

## Worst-case Planting Map (hot-dry)

```{r planting-basemap}
base_map <- get_tiles(site_poly, provider = "Esri.WorldImagery", crop = TRUE, zoom = 18)
```

```{r planting-map-worst, fig.width=8, fig.height=8}
worst_sites <- terra::crop(union_worst, site_poly)
levels(worst_sites) <- c(FALSE, TRUE)

ggplot() +
  geom_spatraster_rgb(data = base_map, interpolate = TRUE, maxcell = Inf) +
  geom_spatraster(data = worst_sites) +
  scale_fill_discrete(na.value = "transparent") +
  geom_sf(data = site_poly, fill = NA, lwd = 1.5, color = "lightblue") +
  labs(
    title = glue("{display_name}: worst-case (hot-dry) planting locations"),
    fill = "Selected"
  ) +
  theme_minimal()
```

## Best-case Planting Map (warm-dry)

```{r planting-map-best, fig.width=8, fig.height=8}
best_sites <- terra::crop(union_best, site_poly)
levels(best_sites) <- c(FALSE, TRUE)

ggplot() +
  geom_spatraster_rgb(data = base_map, interpolate = TRUE, maxcell = Inf) +
  geom_spatraster(data = best_sites) +
  scale_fill_discrete(na.value = "transparent") +
  geom_sf(data = site_poly, fill = NA, lwd = 1.5, color = "lightblue") +
  labs(
    title = glue("{display_name}: best-case (warm-dry) planting locations"),
    fill = "Selected"
  ) +
  theme_minimal()
```

# Session Info

```{r session-info}
sessionInfo()
```
